Spatial Reasoning and Statistical Graphics

### 2014-10-30 Paper/Draft1/TestingVisualAptitude.Rnw
small edits

@@

<<ResultsScaledScores, echo=F, include=T, fig.pos="hbt", fig.cap="Test scores for lineups and visuospatial tests. As none of the participants scored at or below zero, we can conclude that there is little evidence of random guessing. We also note the score compression that occurs on the Visual Search test; this indicates that most participants scored extremely high, and thus, participants' scores are not entirely representative of their ability. \\label{fig:Scores}", fig.width=4.5, fig.height=4.5, out.width='\\linewidth', warning=F, message=F>>=

>>>>

\comment{Next few steps for the analysis: (1) I think we should add a linear model for lineup scores that includes the demographics of participants as well; (2)}

@@

<<ResultsScaledScores, echo=F, include=T, fig.pos="hbt", fig.cap="Test scores for lineups and visuospatial tests. As none of the participants scored at or below zero, we can conclude that there is little evidence of random guessing. We also note the score compression that occurs on the Visual Search test; this indicates that most participants scored extremely high, and thus, participants' scores are not entirely representative of their ability. \\label{fig:Scores}", fig.width=4.5, fig.height=4.5, out.width='.\\linewidth', warning=F, message=F>>=
